Efficient Handling of String-Number Conversion

### 2019-11-22 draft.tex
sec 6

The correctness of the entire construction of $\underf \dr {\insc}$ is expressed by  Theorem~\ref{theorem:correct}. 
It uses the decoding function $\decode \dr$ parameterized by the domain restriction $\dr$. 
The $\decode \dr$ function maps a word encoding $I_e: V_\dr\cup\#V_\dr\rightarrow \nat$ paired with an interpretation of integer variables $I_z$ to a model $I_s \cup I_z$ of a string constraint. 
Formally, 
$\decode  \dr (I_e\cup I_z) = \{I_s \cup I_z \mid \forall x\in X: I_s(x) = \decode {\dr(x)} ((I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}})\}$.
The condition says each string variable $x$ is interpreted as the ${\dr(x)}$-decoding of the word encoding $(I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}}$.
We define the output of $\decode  \dr (I_e\cup I_z)$ as a set so that \emph{invalid word encodings}, i.e. those do not corresponds to possible word encodings from PFAs, are mapped to empty sets and valid ones are mapped to singleton sets.
We define the $\dr$-encoding function as the counterpart of $\dr$-decoding,  
%
namely, for a model $I_s \cup I_z$ of a string constraint,  
we let $\encode \dr (I_s \cup I_z) \defeq \{I_e\cup I_z\mid \decode \dr (I_e\cup I_z) = I_s \cup I_z \}$.
We lift $\decode \dr$ and $\encode \dr$ to sets of interpretations in the standard manner.
\begin{theorem}\label{theorem:correct}
$\decode \dr (\semof {\underf \dr {\insc}}) = \semof{\insc}^\dr$ 
\end{theorem}

>>>>

The correctness of the entire construction of $\underf \dr {\insc}$ is expressed by  Theorem~\ref{theorem:correct}. 
It uses the decoding function $\decode \dr$ parameterized by the domain restriction $\dr$. 
The $\decode \dr$ function maps a \emph{ many-words encoding} $I_e: V_\dr\cup\#V_\dr\rightarrow \nat$ paired with an interpretation of integer variables $I_z$ to a model $I_s \cup I_z$ of a string constraint. Note that the many-words encoding $I_e$ is a union of ${\dr(x)}$-encodings for all $x$ in $X$.
Formally, 
$\decode  \dr (I_e\cup I_z) = \{I_s \cup I_z \mid \forall x\in X: I_s(x) = \decode {\dr(x)} ((I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}})\}$.
The condition says each string variable $x$ is interpreted as the ${\dr(x)}$-decoding of the word encoding $(I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}}$.
%We define the output of $\decode  \dr (I_e\cup I_z)$ as a set so that \emph{invalid word encodings}, i.e. those do not corresponds to possible word encodings from PFAs, are mapped to empty sets and valid ones are mapped to singleton sets.
We define the $\dr$-encoding function as the counterpart of $\dr$-decoding,  
%
namely, for a model $I_s \cup I_z$ of a string constraint,  
we let $\encode \dr (I_s \cup I_z) =\{I_e\cup I_z\mid \decode \dr (I_e\cup I_z) = I_s \cup I_z \}$.
We lift $\decode \dr$ and $\encode \dr$ to sets of interpretations in the standard manner.
\begin{theorem}\label{theorem:correct}
$\decode \dr (\semof {\underf \dr {\insc}}) = \semof{\insc}^\dr$ 
\end{theorem}
